---
output:
  github_document:
    html_preview: true
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
```{r, echo=FALSE, results='asis'}
#bcgovr::insert_bcgov_devex_badge("Exploration")
```
[![License](https://img.shields.io/badge/License-Apache%202.0-blue.svg)](https://opensource.org/licenses/Apache-2.0)

# Wetland_SkeenaESI_Monitoring
This repository presents 3 analysis; 1) Set of scripts that read in the Skeena East Environmental Stewardship Initiative's (ESI) Wetland Ecosystem Services Protocol (WESP) 2019 field cards, cleanup and summarize; 2) Generate a list of potential 2020 wetlands to sample, stratified based on groupings of Biogeoclimatic Ecosystem Classification (BEC) zones and selected to capture range of wetland flow characterizations, adjacent land type and disturbance; and 3) compiles Tier 1.5 wetland date, specifically indicators downloaded from Climate BC and landform position.

### Data
Field data was collected in 2019 by Skeena East ESI crews. Paper forms were transferred onto excel spreadsheets.

Data on wetlands was collated by Jesse Fraser using provincial and regional inventory. Skeena-Stikine FLNRORD District office supplied an updated roads layer - available upon request.

Raster Land type, forest age and human footprint ESI specific layers used in this analysis are also available upon request

ClimateBC variables - http://climatebc.ca

Landform data from Adaptwest's landfacets https://adaptwest.databasin.org/pages/adaptwest-landfacets


### Usage
There are three sets of scripts that are contained in the repo, they need to be run in order, note there is some duplication between sets*:

Plot Data processing:

- plot_01_load_2019.R
- plot_02_clean_data.R
- data is then passed to Wet_03_analysis_6_samplePrep.R

Sample selection:

- Wet_01_load_spatial.R*
- Wet_02_clean_1_spatial.R*
- Wet_02_clean_2_spatial_AddWshds.R
- Wet_02_clean_3_spatial_AddFREP.R
- Wet_02_clean_4_spatial_AddCGL.R
- Wet_03_analysis_1_AdminUnits.R
- Wet_03_analysis_2_BECStrata.R
- Wet_03_analysis_3_FlowStrata.R
- Wet_03_analysis_4_LandTypeStrataN.R
- Wet_03_analysis_5_DisturbanceStrataN.R
- Wet_03_analysis_6_samplePrep.R
- Wet_03_analysis_7_2019_ReportCard.R
- Wet_03_analysis_8_sampleRequirements.R
- Wet_03_analysis_9_sampleAddStrata.R
- Wet_03_analysis_10_2020_ReportCard.R
- Wet_03_analysis_11_sample2020PickNewSite.R
- Wet_03_analysis_12_2020SiteAdjust.R
- Wet_03_analysis_13_sample2020RevisedSummary.R
- Wet_04_output_1.R*
- Wet_04_output_2.R

Tier 1.5 wetland data:

- Wet_01_load_spatial.R*
- Wet_02_clean_1_spatial.R*
- Tier1.5_03_analysis.R
- Wet_04_output_1.R*

*used for multipled tasks

### Project Status
This project is part of Skeena East ESI a collaboration of Skeena First Nations and the Provincial Government.

### Getting Help or Reporting an Issue

To report bugs/issues/feature requests, please file an [issue](https://github.com/bcgov/Wetland_SkeenaESI_Monitoring/issues/).

### How to Contribute

If you would like to contribute, please see our [CONTRIBUTING](CONTRIBUTING.md) guidelines.

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.

### License

```
Copyright 2020 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the &quot;License&quot;);
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an &quot;AS IS&quot; BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
```

---
This repository is maintained by [ENVEcosystems](https://github.com/orgs/bcgov/teams/envecosystems/members). 
